\sys: Controllable Program Regeneration

### 2025-06-10 paper/draft.tex
Remove time overhead
Signed-off-by: Evangelos Lamprou <vagos@lamprou.xyz>

\sys consistently satisfies more of the declared properties while avoiding unintended behaviors. For instance, in the \texttt{flatmap-stream} benchmark, GPT-4 often preserved malicious side effects when the code appeared innocuous, whereas \sys generated provably pure rewrites by treating the source as untrusted and grounding regeneration in I/O behavior alone.

\heading{Planning overhead}
We measure the time taken by \sys's logic engine to select the minimal set of
properties required to satisfy each query. 
\begin{table}[h]
  \centering
  \caption{Planning overhead: time taken by \sys's logic engine to compute minimal property set.}
  \begin{tabular}{lcc}
    \toprule
    Benchmark & Properties Considered & $T_{\text{plan}}$ (ms) \\
    \midrule
    Rosetta Code & \xxx & \xxx \\
    npm Utilities & \xxx & \xxx \\
    Python Utilities & \xxx & \xxx \\
    SSCA & \xxx & \xxx \\
    Microbenchmarks & \xxx & \xxx \\
    \bottomrule
  \end{tabular}
\end{table}

Across all benchmarks, the planning step completes in under \xxx ms on average.
% TODO: re-add this
% adding negligible latency compared to synthesis time. Moreover, by minimizing
% the number of properties to extract and verify, planning reduces the total time
% and resource usage of the regeneration pipeline.

>>>>

\sys consistently satisfies more of the declared properties while avoiding unintended behaviors. For instance, in the \texttt{flatmap-stream} benchmark, GPT-4 often preserved malicious side effects when the code appeared innocuous, whereas \sys generated provably pure rewrites by treating the source as untrusted and grounding regeneration in I/O behavior alone.
Across all benchmarks, the planning step completes in under \xxx ms on average.
% TODO: re-add this
% adding negligible latency compared to synthesis time. Moreover, by minimizing
% the number of properties to extract and verify, planning reduces the total time
% and resource usage of the regeneration pipeline.
